---
title: "index.Rmd"
author: "Group H6"
date: "5/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(knitr)
source("summary.R")
source("summarytable.R")
```

## Introduction

For our final project, we have decided to take an interest into and analyze the Olympic Games, both summer and winter. Considering that these events have been occurring for over a century, as well as the fact that everyone in our group enjoys watching the Olympics, this domain was an easy and interesting topic for analysis. In our selected dataset "120 Years of Olympic History", listed are every single athlete that has ever competed in an Olympic event since 1896, and includes their height and weight, their sex, what country they competed for, the events they competed in, and what medal they won, if any. The set additionally contains information about the games themselves, like what city the events were held in, whether they were Summer or Winter Olympics, and the year the Games were held in. 

## Summary Information

 - In total, there have been `r total_ath` athletes that have competed in the modern Olympic Games.
 - `r male`% of Olympic athletes have been male, and `r female`% have been female.
 - There have been a total of `r sum_medal` medals won, with `r medals[2, 2]` gold, `r medals[3, 2]` silver, and `r medals[1, 2]` bronze.
 - Over its 120 year history, the Games have hosted over `r total_sports` unique sports and `r total_events` events.
 - `r unique_city` cities have hosted at least once, `r two_host` cities have hosted two or more times, and only `r three_host` cities have hosted three times. 

## Aggregated Table

Below is a table of the top 20 countries all-time in medal counts:

```{r, echo = F}
kable(table)
```

From this table, we can see that the US is far and away the most dominant country in terms of medals, with a serious gap over the second place, and now collapsed Soviet Union (over doubled the medal count!).